---
title       : Miles per gallon
subtitle    : year of 1999 and 2008
author      : GG Choi
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft}
---

## Graphes

You can choose graphes discribed as below.

1. scatter plot of highway milage against engine displacement
2. boxplot by class
3. scatter plot of highway milage against engine displacement by manufacturers

Additionally you can choose years such as 1999, 2008 and both years

----

## 1. by engine size

This selection shows scatter plot of highway mpg against engine displacement. 

```{r, fig.height=5, fig.aligh='center', message=F, echo=FALSE}
require(ggplot2)
ggplot(mpg,aes(hwy,displ,color=factor(cyl)))+geom_point(aes(shape=factor(year)))
```

-----

## 2. boxplot by class

This selection shows boxplot of highway mpg by car class


```{r, fig.height=5, fig.aligh='center', message=F, echo=FALSE}
require(ggplot2)
ggplot(mpg,aes(class,displ,color=factor(cyl)))+geom_boxplot(aes(shape=factor(year)))
```

-----

## 3. by manufacturer

This selection shows scatter plot of highway mpg by car manufacturer


```{r, fig.height=5, fig.aligh='center', message=F, echo=FALSE}
require(ggplot2)
ggplot(mpg,aes(hwy,displ,color=factor(cyl)))+geom_point(aes(shape=factor(year)))+facet_wrap(~manufacturer)
```



